---
title: "mqreportr"
author: "Michal Rackiewicz"
format: html
server: shiny
---

## Shiny Documents

This Quarto document is made interactive using Shiny. Interactive documents allow readers to modify parameters and see the results immediately. Learn more about Shiny interactive documents at <https://quarto.org/docs/interactive/shiny/>.

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive:

```{r}
# Load packages
# library(BiocManager)
# library(limma) #loess normalization
# library(missForest) #amputation
library(mixomics) #NIPALS PCA
library(randomForest) #imputation
# library(shiny)
library(tidyverse)
```

# Functions
## Parse files
```{r}
mq_output <- "data-raw/"
mq_tables <- list.files(mq_output)
site_tables <- NULL
for (t in mq_tables) {
  if (str_detect(t, "Site")){
    site_tables <- append(site_tables, t)
  }
}
# from site_tables user selects sites of interest
```

### Load FASTA file for annotations
```{r}
# Load FASTA file
fasta_path <- file.choose()

```

```{r}
load_table <- function(df, multi) {
  
  cols <- c("Protein IDs",
            "Only identified by site",
            "Reverse",
            "Potential contaminant")
  
  if (multi == "tmt") {
    quant_colums <- paste0("matches(", "^(LFQ) |(I|i)ntensity .*", ")")
    cols <- append(cols, quant_colums)
  } else if (multi == "lfq") {
    quant_colums <- paste0("matches(", "Reporter intensity (corrected|\\d)", ")")
    cols <- append(cols, quant_colums)
  } else {
    quant_colums <- paste0("matches(", "Ratio .*", ")")
    cols <- append(cols, quant_colums)
  }
  
  cols <- cols[grepl("Reporter intensity (corrected|\\d)", cols)]

  df <- readr::read_tsv(file = df,
                        col_select = cols)
  return(df)
}
```

### Universal data cleaning
Formats column names, removes reverse and contaminants 
```{r}
clean_df <- function(data) {
  del_row <- which(data[, "Reverse"] == "+" | data[, "Potential contaminant"] == "+")
  del_col <- which(names(data) %in% c("Reverse", "Potential contaminant"))
  
  data <- data[-del_row, -del_col]
  data <- janitor::clean_names(data, abbreviation = "ID")
  return(data)
}
```

summary from evidence:
total number of sites
enrichment efficiency
peptides sharing modifications

summary from sites:
number of sites
sites/protein
correlations between replicates


NIPALS PCA for initial clustering
imputation:
- msimpute
- missforest
NIPALS PCA
Batch effect correction with ComBat
RUV normalization (identify those proteins which change the least across sample)
Normalization:
- median
- loess
- quantile
output boxplots and MA plots
