---
title: "mqreportr"
author: "Michal Rackiewicz"
format: html
server: shiny
---

## Shiny Documents

This Quarto document is made interactive using Shiny. Interactive documents allow readers to modify parameters and see the results immediately. Learn more about Shiny interactive documents at <https://quarto.org/docs/interactive/shiny/>.

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive:

```{r}
# Load packages
# library(BiocManager)
# library(limma) #loess normalization
# library(missForest) # imputation
library(mixomics) #for NIPALS PCA
# library(shiny)
library(tidyverse)
```

```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r}
#| context: server
output$distPlot <- renderPlot({
   x <- faithful[, 2]  # Old Faithful Geyser data
   bins <- seq(min(x), max(x), length.out = input$bins + 1)
   hist(x, breaks = bins, col = 'darkgray', border = 'white',
        xlab = 'Waiting time to next eruption (in mins)',
        main = 'Histogram of waiting times')
})
```

Parse files
```{r}
mq_output <- "data-raw/"
mq_tables <- list.files(mq_output)
site_tables <- NULL
for (t in mq_tables) {
  if (str_detect(t, "Site")){
    site_tables <- append(site_tables, t)
  }
}
# from site_tables user selects sites of interest
```

```{r}
# Load FASTA file
fasta_path <- file.choose()

```
summary from evidence:
total number of sites
enrichment efficiency
peptides sharing modifications

summary from sites:
number of sites
sites/protein
correlations between replicates




NIPALS PCA
imputation:
- msimpute
- missforest
NIPALS PCA
Batch effect correction with ComBat
RUV normalization (identify those proteins which change the least across sample)
Normalization:
- median
- loess
- quantile
output boxplots and MA plots
