---
title: "mqreportr"
author: "Michal Rackiewicz"
format: html
server: shiny
---

## Shiny Documents

This Quarto document is made interactive using Shiny. Interactive documents allow readers to modify parameters and see the results immediately. Learn more about Shiny interactive documents at <https://quarto.org/docs/interactive/shiny/>.

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive:

```{r}
# Load packages
# library(shiny)
library(tidyverse)
```


```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r}
#| context: server
output$distPlot <- renderPlot({
   x <- faithful[, 2]  # Old Faithful Geyser data
   bins <- seq(min(x), max(x), length.out = input$bins + 1)
   hist(x, breaks = bins, col = 'darkgray', border = 'white',
        xlab = 'Waiting time to next eruption (in mins)',
        main = 'Histogram of waiting times')
})
```

Parse files
```{r}
wd <- setwd(getwd())
mq_tables <- list.files(wd)
site_tables <- NULL
for(table in mq_tables){
   if (grep("Site", table[i])){
      append(site_tables, table[i])
   }
}
```

```{r}
load_data <- function(file_path){
  files_input <- list.files(path = file_path)
  tables <- apply(files_input, str_extract, pattern = "^(.+)Sites")
  
  for (i in filenames) {
    filename
  }
  
}
```

